The pollination trade-off

### 2019-03-07 paper/supp-info.Rmd
Make fig. supp info. distribution of effects clearer and larger

```{r fig-model-results, fig.height = 7, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Only results for the models with the most parsimonous fixed effects.", eval=T}
drake::readd(fig_all_model_results)
```

>>>>

```{r fig-model-results, fig.height = 9, fig.cap = "Distribution of effect estimates for models of conspecific and heterospecific pollen density gain. Model formulas have been abbreviated: *a* for abundance, *k* for the number of shared polinators, *p* for the visit effectiveness, and *t* for trait originality.", eval=T}
drake::readd(fig_all_model_results)
```
